Using reference models in variable selection \vspace{.1in}

### 2020-07-06 paper/ref_approach.tex
minor edit of contributions

This paper is structured as follows. In Section
\ref{ref-intro}, we review the concept of the reference
model, its benefits with examples and how it can be used as a filter
on data in a simple way. In Section \ref{comparison-minimal-subset} and 
Section \ref{comparison-complete-subset}, we show the
benefits of a reference model approaches for minimal and complete 
variable selection, respectively, before we end with a conclusion in Section \ref{conclusion}.

>>>>

The main contributions of our work are:

\begin{itemize}
\item we show a simple and basic way to frame any variable selection method in the reference model approach,
\item we make a structured comparison for variable selection methods with or without using a reference model, both for the the complete and the minimal subset selection,
\item and we provide evidence in supporting the projection predictive approach as a principled way to use the reference model.
\end{itemize}

The paper is structured as follows. In Section
\ref{ref-intro}, we review the concept of the reference
model, its benefits with examples and how it can be used as a filter
on data in a simple way. In Section \ref{comparison-minimal-subset} and 
Section \ref{comparison-complete-subset}, we show the
benefits of a reference model approaches for minimal and complete 
variable selection, respectively, before we end with a conclusion in Section \ref{conclusion}.
